---
title: "Put a real title here"
subtitle: "SDS 192: MP4"
author: 
- name: Author One
  affiliation: Smith College
- name: Author Two
  affiliation: Smith College
date: "`r format(Sys.Date(), '%B %e, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    fig_width: 8
    fig_height: 8
    fig_caption: true
    theme: lumen
    df_print: paged
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  echo = TRUE,
  warning = FALSE
)
library(tidyverse)
library(sds192)
library(sf)
```

## Introduction

> READ THE INSTRUCTIONS: https://beanumber.github.io/sds192/mod_spatial.html


## Loading the data

```{r, message=FALSE}
library(macleish)
names(macleish_layers)
```

## Static maps

You can make a basic static map with **ggplot2** using `geom_sf()`, as shown in the figure below.

```{r static, fig.cap="The boundary of the MacLeish property."}
boundary <- macleish_layers %>%
  pluck("boundary")

ggplot() +
  geom_sf(data = boundary)
```

## Dynamic maps

You can make a basic dynamic map with **leaflet**, as shown in the figure below.

```{r dynamic, fig.cap="The boundary of the MacLeish property."}
library(leaflet)

leaflet() %>%
  addTiles() %>%
  addPolygons(data = boundary)
```



## Word count

```{r word_count, message=FALSE, echo=FALSE}
text_stats()
```

## Standards

In this assignment, we attempted the following [standards](https://beanumber.github.io/sds192/standards.html):

- `r standard_button("wrangling")`: We met the Wrangling standard because we...
- `r standard_button("spatial")`: We met the Spatial standard because we...
- `r standard_button("leaflet")`: We met the Leaflet standard because we...
- `r standard_button("aesthetics")`: We mastered the Aesthetics standard because we...
- `r standard_button("markdown")`: We mastered the R Markdown standard because we...

## References
